%-------------------------
% Resume in Latex
% Rasool Peykarporsan
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}

\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
    \bfseries \vspace{2pt} \raggedright \large
}{}{0em}{}[\color{light-grey}{\titlerule[2pt]} \vspace{-4pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-1pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\
      \textit{#3} & {\color{dark-grey}\small #4}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Rasool Peykarporsan} \\ \vspace{5pt}
    \small
    \faGlobe \hspace{2pt} \href{https://rasoolpeykarporsan.me/}{\texttt{rasoolpeykarporsan.me}} \hspace{1pt} $|$
    \hspace{1pt} \faPhone* \hspace{1pt} \texttt{+64 29 023 55104} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \href{mailto:Rasool.peykarporsan@gmail.com}{\texttt{Rasool.peykarporsan@gmail.com}} \\
    \faGithub \hspace{2pt} \href{https://github.com/Rasoolpey}{\texttt{Rasoolpey}} \hspace{1pt} $|$
    \hspace{1pt} \faGraduationCap \hspace{2pt} \href{https://scholar.google.com/citations?user=AWOKpCAAAAAJ}{\texttt{Google Scholar}} \hspace{1pt} $|$
    \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{44 Symonds Street, Grafton, Auckland, New Zealand}
    \\ \vspace{-3pt}
\end{center}

\vspace{5em}


Kia ora, \\[15pt]

I am writing to express my interest in the Power System Design and Integration (HWEE) Intern position within the Wireless Power Technology team at Apple. I am currently pursuing my PhD in Power Electronics \& Power Systems at Auckland University of Technology. With a strong theoretical and practical background spanning analog and digital circuit design, I have developed a solid technical foundation in power systems and electronics. My PhD research and project experience have enhanced my expertise in resonant converters, impedance matching, and direct wireless charging with hands-on experience on designing and custom-winding inductors, chokes, and transformers across a variety of core types to optimize power transfer efficiency. I am well skilled in using MATLAB, LTspice, and Cadence for circuit-level simulation and modeling, which has prepared me to tackle new circuit or power technology proof-of-concept investigations. \\[10pt]

During my time at AUT and as the founder of Circuit Intelligent, I was fortunate to gain extensive hands-on experience designing and building modular microgrid hardware testbeds. I frequently utilize Python and MATLAB for data collection, scripting, and doing hardware in the loop test. In these projects, I supported prototyping, system bring-up, and characterization using instrumentation like oscilloscopes, VNAs, Opal-RT and micro controllers like stm32f4/f7 and  Texas Instruments C2000. During my PhD I collaborated with multidisciplinary peers and learned how proactive failure analysis, root cause investigations, and rigorous Design of Experiments (DOE) could prevent costly delays. Over time, I have developed a deep passion for solving production system-level problems and bridging the gap between design intent and physical, working hardware.\\[10pt]

What draws me to Apple is your commitment to build top notch quality hardware products. I am particularly inspired by the mission of the Wireless Power Technology team to advances wireless charging designs that enhance the user experience for Apple's products. As a highly self-motivated individual passionate about contributing to meaningful technological advancements, I find Apple's dynamic environment, which cultivates creativity, partnership, and fresh ways of thinking about old problems, deeply motivating. I am excited about the opportunity to work alongside a team that promotes engineering excellence and innovation, and to help deliver the next groundbreaking wireless power technology. \\[10pt]

I would welcome the opportunity to discuss how my background and aspirations align with Apple's goals. Enclosed is my CV for your reference. Thank you for considering my application. I look forward to the possibility of contributing to your innovative projects. \\[15pt]

Ngā mihi nui, \\[10pt]
Rasool Peykarporsan\\[10pt]
28th April 2026 
\end{document}
